animbook: Visualizing changes in performance measures and demographic affiliations using animation

### 2023-10-29 animbook-journal.Rmd
tidied up the osiris paragraph

  From the kangaroo plot (Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:kan-osiris-figure}','\\@ref(fig:kan-osiris-gif)'))`), most companies are staying in the same quantile group, with only a small number moving upward or downward. Most of the movement is made by American companies, supporting the OECD report (@oecd_report) that the United States has a higher turnover rate compared to Japan. To emphasize this point, the wallaby plot can be utilized (Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:osiris-figure}','\\@ref(fig:osiris-gif)'))`), this reinforces that there are more American companies de-listed compared to Japanese companies. There could be various reasons for this trend, such as the absence of Japanese companies in the Top 25% in 2006 or the possibility that Japanese companies who started in the Top 25% in 2006 were not de-listed.

>>>>

  From the kangaroo plot (Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:kan-osiris-figure}','\\@ref(fig:kan-osiris-gif)'))`), most companies are staying in the same quantile group, with only a small number moving upward or downward. Most of the movement is made by American companies, supporting the OECD report (@oecd_report) that the United States has a higher turnover rate compared to Japan. To emphasize this point, the wallaby plot can be utilized (Figure `r knitr::asis_output(ifelse(knitr::is_latex_output(), '\\ref{fig:osiris-figure}','\\@ref(fig:osiris-gif)'))`). There are clearly more American companies de-listed compared to Japanese companies, and we can see that there are no Japanese companies in the Top 25% in 2006 that were de-listed.
